### 2020-05-06 thesis/thesis.tex
Minor extensions to table of contents
Short comments about chapters in thesis

% Opcje klasy 'iithesis' opisane sa w komentarzach w pliku klasy. Za ich pomoca
% ustawia sie przede wszystkim jezyk i rodzaj (lic/inz/mgr) pracy, oraz czy na
% drugiej stronie pracy ma byc skladany wzor oswiadczenia o autorskim wykonaniu.
\documentclass[declaration,shortabstract]{iithesis}

@@

%%%%% DANE DO STRONY TYTUŁOWEJ
% Niezaleznie od jezyka pracy wybranego w opcjach klasy, tytul i streszczenie
% pracy nalezy podac zarowno w jezyku polskim, jak i angielskim.
% Pamietaj o madrym (zgodnym z logicznym rozbiorem zdania oraz estetyka) recznym
% zlamaniu wierszy w temacie pracy, zwlaszcza tego w jezyku pracy. Uzyj do tego
% polecenia \fmlinebreak.
\polishtitle    {Efekty koalgebraiczne oraz ich kohandlery \fmlinebreak w językach programowania}
\englishtitle   {Coalgebraic effects and their cohandlers \fmlinebreak in programming languages}
\polishabstract {
    \ldots
}
\englishabstract{
    \ldots
}
\author         {Mateusz Urbańczyk}
\advisor        {dr Maciej Piróg}
\date           {30 czerwca 2020}                     % Data zlozenia pracy
% Dane do oswiadczenia o autorskim wykonaniu
% \transcriptnum {291480}                     % Numer indeksu
% \advisorgen    {dr. Macieja Piróga} % Nazwisko promotora w dopelniaczu
%%%%%

@@

In this thesis we present experimental programming language Freak, which is an
implementation of Continuation Passing Style for Effect Handlers paper \cite{handlers-cps},
with the addition of a few basic constructs. We start by presenting the related work,
then discuss syntax and operational semantics. Basic usage guide for playing with
the language is provided, as well as implementation details and examples. We conclude
by stating what are the possible augmentations, that are intended to be made in the future.

\section{Problem Analysis}
\section{Problem Statement}
\section{Thesis Outline}

\chapter{Background}
\section{Algebraic Effects}
\section{Categorical Setting for Universal Algebra}
\section{Comodels and Duality}

\chapter{Proposed Solutions}
\section{Dynamic Constraints Checking}
\section{Linear Types}
\section{Data-Flow Analysis}
\section{Cohandlers as a Separate Construct}
\section{Related Work}

@@

\chapter{Coeffectful Programming with Cohandlers}
\section{Examples}
\label{sec:examples}
    In this section we present a few examples to show the capabilities of the
    language. The ideas have been based on \cite{programming-in-eff}, and thus will not be
    described in great details. More exemplary programs in Freak language can
    be found under \\ \href{https://github.com/Tomatosoup97/freak/tree/master/src/programs}{\underline{https://github.com/Tomatosoup97/freak/tree/master/src/programs}}.

@@

    \subsection{Side effects}

@@

\section{Coexamples}
    \ldots

@@

    As of this day, two implementations are available, one based on the curried
    translation and Appel \cite{appel-continuations}, and the second one based
    directly on the uncurried translation with continuations as explicit stacks
    from paper. More details can be found in section \ref{sec:implementation}.
    All commands are available within \verb src  directory.

@@

    \section{Abstract Syntax Trees}
    \label{sec:implementation-ast}

@@

@@

    \section{Type System}
    \ldots

@@

\chapter{Conclusion}
\section{Summary}
    \ldots
\section{Future work}

    \subsection{Alternative evaluation}

@@

    \subsection{Type inference}

@@

    \subsection{Multiple instances of algebraic effect}

@@

%%%%% BIBLIOGRAFIA

% \begin{thebibliography}{1}
% \bibitem{example} \ldots
% \end{thebibliography}

>>>>

\documentclass[declaration,shortabstract]{iithesis}

@@

%%%%% DANE DO STRONY TYTUŁOWEJ
\polishtitle    {Efekty koalgebraiczne oraz ich kohandlery \fmlinebreak w językach programowania}
\englishtitle   {Coalgebraic effects and their cohandlers \fmlinebreak in programming languages}
\polishabstract {
    \ldots
}
\englishabstract{
    \ldots
}
\author         {Mateusz Urbańczyk}
\advisor        {dr Maciej Piróg}
\date           {30 czerwca 2020}                     % Data zlozenia pracy
% Dane do oswiadczenia o autorskim wykonaniu
% \transcriptnum {291480}                     % Numer indeksu
% \advisorgen    {dr. Macieja Piróga} % Nazwisko promotora w dopelniaczu
%%%%%

@@

% TODO This requires a rework
In this thesis we present experimental programming language Freak, which is an
implementation of Continuation Passing Style for Effect Handlers paper \cite{handlers-cps},
with the addition of a few basic constructs. We start by presenting the related work,
then discuss syntax and operational semantics. Basic usage guide for playing with
the language is provided, as well as implementation details and examples. We conclude
by stating what are the possible augmentations, that are intended to be made in the future.

\section{Problem Analysis}

What are the issues with normal algebraic effects?

\section{Problem Statement}

Brief and concise description of the problem

\section{Thesis Outline}

\chapter{Background}
\section{Algebraic Effects}

What are algebraic effects?

\section{Categorical Setting of Universal Algebra}

For the purpose of describing the duality between algebra and coalgebra,
we allow ourselves to wander a bit deeper into category theory.

    \subsection{Algebraic Theories}

    Sigma-Signatures, Sigma-Terms, Sigma-Equations, Interpretations, Models, Free models

    \subsection{Free models form monads}

    Maybe not a subsection but just a lemma

    \subsection{Models homomorphisms}

    T-homomorphisms with respect to theory T

    \subsection{Parametrized operations}

\section{Duality}
    \subsection{Comodels}

    Comodel in $\mathcal{C}$ is just a Model in $ \mathcal{C}^{op} $.

    Models -- Worlds

    \subsection{Cooperations}

    Derive from Models duality

    \subsection{Coalgebraic Effects}

\section{Related Work}
    \subsection{Algebraic Effects}

@@

    \subsection{Coalgebraic Effects}

    Ahman and Bauer \cite{runners-in-action}

\chapter{Potential Solutions}

One-shot continuations

\section{Dynamic Constraints Checking}

\section{Linear Types}

Solve the issue through introduction of linear type system.

\section{Data-Flow Analysis}

Another static analysis of the program.

\section{Cohandlers as Separate Constructs}

Simplify semantics by separating coalgebraic effects into a new, restricted
construct in programming language

\chapter{Effectful and Coeffectful Programming}
\section{Examples}
\label{sec:examples}
    In this section we present a few examples to show the capabilities of the
    language. The ideas have been based on \cite{programming-in-eff}, and thus will not be
    described in great details. More exemplary programs in Freak language can
    be found under \\ \href{https://github.com/Tomatosoup97/freak/tree/master/src/programs}{\underline{https://github.com/Tomatosoup97/freak/tree/master/src/programs}}.

@@

    \subsection{Taming Side effects}

@@

\section{Coexamples}

    Examples for cohandlers

@@

    % Outdated
    As of this day, two implementations are available, one based on the curried
    translation and Appel \cite{appel-continuations}, and the second one based
    directly on the uncurried translation with continuations as explicit stacks
    from paper. More details can be found in section \ref{sec:implementation}.
    All commands are available within \verb src  directory.

@@

    \section{Abstract Syntax Tree}
    \label{sec:implementation-ast}

@@

    \section{Target calculus}

@@

@@

\chapter{Conclusion}
\section{Summary}

    What was achieved, what was described, what needs to be done or researched.

\section{Future work}

    \subsection{Abstract machine}

@@

    \subsection{Type inference and row polymorphism}

@@

    \subsection{Multiple instances of algebraic effects}

@@

%%%%% BIBLIOGRAPHY
